International Relations are a Social Network:\\ A Latent Network Approach for Global Politics

### 2017-10-19 paper/4_app.tex
working it

\begin{table}
\caption{Features of the Studies Replicated. }
	\begin{tabular}{lcccccc}
& Model & N. Actors & Years  & N. Dyads & Dyads Type & Clustering $\sigma_{\hat{\beta}}$ \\ \toprule
Reiter \& Stam (2003) & Logit & & & $753,456$ & Directed & Robust \\	McDonald (2004) & Logit & & & $92,354$ & Undirected & Robust\\
Rose (2004) & OLS & ? &  ?& $234,597$ & Directed & Robust \\	 
Weeks (2012) & Logit & ? & ?& $901,540$ & Directed & Robust \\
Gibler (2017) & Logit & 21,275 & 193 & $650,557$ & UnDirected & no \\ \bottomrule
	\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Features of the Studies Replicated. }
	\begin{tabular}{lcccccc}
& Model &  N. Actors  & N. Dyads & Dyads Type & Clustering $\sigma_{\hat{\beta}}$ \\ \toprule
Reiter \& Stam (2003) & Logit & 193 & $753,456$ & Directed & Robust \\	
McDonald (2004) & Logit & 198 & $92,354$ & Undirected & Robust\\
Rose (2004) & OLS & 177 & $234,597$ & Directed & Robust \\	 
Weeks (2012) & Logit & 197 &  $901,540$ & Directed & Robust \\
Gibler (2017) & Logit & 193 &    & $650,557$ & UnDirected & none \\ \bottomrule
	\end{tabular}
\end{table}
